\chapter*{Abstract}
\centerline{Application with GUI for discrete signal analysis}
\vspace{0.5cm}
\indent Signals surround us in many aspects of life, from telecomunications to medicine and stock market investments. The purpose of this project is to create advanced python tool for analyzing discrete signals using a wide spectrum of numerical tools.  \\
\indent The first part of the work is about signals. There is introduction about what signals are and some basic tools for their analysis are described. \\
\indent The second part consist details about the chosen popular signal analysis methods. One chapter is devoted to detecting the transformation of time domain signals into the domain of frequencies contained in a signal using Fourier transform. And next chapter introduces the technical analysis wchich is used to detect investments signals and its interpretation. \\
\indent  The last part of this paper is abut the implementation of the tool for analyzing discrete signals using python tool. The chapter introduces the tools that are used in a project, it is Pycharm Anaconda and Jupyter Notebook. Next there are presented the libraries used in the project. The chapter also consist hardware requirements and installation description of the mentioned environment. Finally, there is presented the interface of the created tool and the user manual.\\
\vspace{0.5cm}\newline
\textbf{Keywords:} signals, digital signals, discrete signals, investments, Pycharm Anaconda, Jupyter Notebook, Fourier transformation, technical analysis, indicators \vspace{0.5cm}

\noindent \textbf{Field of science and technology, according to requirements of OECD:} engineering and technology, electrical engineering, electronic engineering, information engineering